---
title: "Conseil Scientifique PNA Lynx"
#description: "A two-day workshop"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```


Composition :   
Date de création : xx  
Missions : 
Contact : 

# Timeline

- Day 1
   - Getting familiar with individual-based models (IBMs)
   - Getting familiar with `NetLogoR`
   - Understanding simple models coded in `NetLogoR`
- Day 2
   - Understanding more complex models coded in `NetLogoR`
   - Debugging IBMs
   - Parameterizing IBMs
   - Publishing IBMs
   - Coding on your own

# Requirements

* Install [`R`](https://cloud.r-project.org/) and [`RStudio`](https://rstudio.com/products/rstudio/download/#download)

* Install the following `R` packages: `NetLogoR`, `testthat`. You can install them all at once by running the following code in the `R` command line:

```{r eval = FALSE, echo = TRUE}
install.packages(c("NetLogoR", "testthat"))
```

* You need to be familiar with `R`. This workshop is not about learning how to code on `R` but how to use an `R` package in particular. For example, you need to be familiar with for loops and how to create function (even if they are very simple ones).  

### For any help before or after the workshop

Sarah Bauduin: sarah.bauduin@ofb.gouv.fr



<!-- ## Corrections {.appendix} -->

<!-- If you see mistakes or want to suggest changes, please [create an issue](https://github.com/oliviergimenez/reproducible-science-workshop/issues) on the source repository. -->

<!-- ## Reuse {.appendix} -->

<!-- Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://github.com/oliviergimenez/reproducible-science-workshop/blob/master/LICENSE.md).  -->
